%-------------------------
% Resume in Latex
% Author : Siddharth Jain
% Inspired by: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\usepackage{setspace} % for line spacing

\input{glyphtounicode}

% Custom font
\usepackage{times}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[margin=0.20in]{geometry}

% Set line spacing
\setstretch{0.9}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{\fontsize{10}{11}\selectfont
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\ 
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small#2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.20in]}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\definecolor{Green}{RGB}{83, 129, 53}
\definecolor{Blue}{RGB}{68, 114, 196}

%Section Format
\titleformat{\section}{\color{Green} \fontsize{16}{18}\bfseries
  \vspace{-6pt}\raggedright
}{}{0em}{}[\color{Black}\titlerule\vspace{-4pt}]

\newcommand{\projectHeadingColor}{\color{Blue}}

\begin{document}

%-------------------------------------------%
%%%%%%  RESUME STARTS HERE  %%%%%

%----------HEADING----------%
\begin{tabularx}{\textwidth}{@{} X r @{}}
    \begin{minipage}[t]{\textwidth}
        \href{https://www.linkedin.com/in/sjain166}{{\color{Blue}\textbf{\Huge \scshape Siddharth Jain}}}
         \hfill 
       \href{sj99@illinois.edu}{\textbf{Email:} \color{Blue}\textit{sj99@illinois.edu}}  $|$ 
        \textbf{Phone:} {\color{Blue} +1 (602) 596-7491} \\[0.5em]
        \textbf{Seeking Early Mobile SWE Roles} \hfill
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/sjain166}{\color{Blue}\textit{/in/sjain166}} $|$ \textbf{GitHub:} \href{https://github.com/sjain166}{\color{Blue}\textit{/sjain166}} \\[0.5em] \hfill
        % \textbf{Urbana, IL (Open To Relocation)} \\[0.2em] \hfill
    \end{minipage}
\end{tabularx}

\vspace{-1em}

%-----------EDUCATION-----------%
\section{\fontsize{14}{12}\selectfont EDUCATION}
    \resumeSubHeadingListStart
    \resumeSubheading
    {University of Illinois Urbana-Champaign (UIUC)}{Expected: December 2025}
    {Master of Computer Science}{}
    \resumeItemListStart
        \resumeItem{Courses Taken: Deep Learning For Computer Vision, Advanced Distributed Computing, Computer Security, Cloud Networking}
    \resumeItemListEnd

    \resumeSubheading
    {Arizona State University (ASU)}{August 2020 -- May 2024}
    {Bachelor of Science in Computer Science}{4.00 GPA}
    \resumeItemListStart
        \resumeItem{Courses Taken: Software Design Principles, Operating Systems, Distributed Systems, Computer Networks, Digital Design}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

\vspace{-1em}

%-----------EXPERIENCE-----------%
\section{WORK EXPERIENCE}
\resumeSubHeadingListStart

    \resumeSubheading
    {Software Engineer Intern}{May 2025 -- August 2025}
    {PayPal}{Scottsdale, AZ}
    \resumeItemListStart
        \resumeItem{Engineered \textbf{Spring Batch} pipeline using \textbf{Java \& Raptor} reducing manual \textbf{SQL} fixes by 90\% and enabling millions of loan reconciliations.}
        \resumeItem{Built idempotent and thread safe batch job architecture resolving data staleness across \textbf{BigQuery} and \textbf{SOR} distributed systems at scale.}
        \resumeItem{Optimized \textbf{BigQuery} slot utilization by 75\%, saving costs while maintaining system performance and increasing loan processing capacity.}
        \resumeItem{Implemented \textbf{Skip Listeners} with concurrent failed record accumulation, performing batch writes achieving 200x faster processing.}
        \resumeItemListEnd

    \resumeSubheading
    {Software Engineering Fellow}{January 2024 -- May 2024}
    {Andbounds}{Remote, USA}
    \resumeItemListStart
        \resumeItem{Led \textbf{CMS \& iOS} app migration projects for e-commerce focused on scanning and selling custom insoles for podiatry patients.}
        \resumeItem{Leveraged TrueDepth sensors and \textbf{Core ML} with TheStandardCyborg library to detect and export 3D foot scans.}
        \resumeItem{Migrated iOS application with 40+ pages from storyboard to \textbf{SwiftUI} leveraging MVVM architecture and CocoaPods as PDM}
        \resumeItem{Integrated 15+ Shopify's Rest APIs to the iOS app to authenticate users, fetch order and user details, export scans, and place orders.}
    \resumeItemListEnd

    \resumeSubheading
    {Software Development Engineer Intern}{May 2023 -- August 2023}
    {Amazon}{San Diego, CA}
    \resumeItemListStart
        \resumeItem{Built automated orchestration with \textbf{Lambda, SQS, Java \& TypeScript} to back-fill a million records, saving developer time by 99\%.}
        \resumeItem{Architected 1-click reusable cloud stack using \textbf{AWS:CDK} to perform batching for downstream services with rate-limited TPS.}
        \resumeItem{Constructed robust error handling mechanism with \textbf{automated retries} for transient errors reducing failure, ensuring 100\% data integrity.}
        \resumeItem{Tested system end-to-end using JUnit5 achieving 100\% code coverage. Deployed real-time monitoring dashboard using \textbf{CloudWatch}.}
    \resumeItemListEnd
      
\resumeSubHeadingListEnd

\vspace{-1em}

%-----------PROJECTS-----------%
\section{PROJECTS}
\resumeSubHeadingListStart
    
    \resumeProjectHeading
    {\projectHeadingColor\textbf{Study Buddy} $|$ {Full-Stack iOS Developer} $|$ \emph{\color{Black}SwiftUI, Firebase, CoreData, C\#}}{}
    \resumeItemListStart
        \resumeItem{Engineered an \textbf{iOS app} leveraging \textbf{MVVM} to facilitate collaboration by providing a platform to search, create, and join study sessions.}
        \resumeItem{Established \textbf{Firebase-Auth}, offering users sign-in options via Email, Google, and Apple for enhanced authentication flexibility.}
        \resumeItem{Implemented local \textbf{(CoreData)} and cloud \textbf{(Firestore)} data storage, ensuring seamless data retention and optimized retrieval processes.}
        \resumeItem{Integrated \textbf{MapKit} to allow users to set study session locations. Streamlined navigation process, ensuring accuracy within a 10m range.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\projectHeadingColor\textbf{PitchPal} $|$ {ML Engineer} $|$ \emph{\color{Black}PyTorch, Torchvision, OpenCV, CNN, MediaPipe}}{}
    \resumeItemListStart
        \resumeItem{Designed and implemented an \textbf{AI-powered multimodal analysis system} that evaluates elevator pitches using speech and facial cues.}
        \resumeItem{Built a nervousness classification model using \textbf{EfficientNet-B0} trained on custom-labeled facial expressions, achieving \textbf{80\% accuracy.}}
        \resumeItem{Integrated eye contact detection using a \textbf{pre-trained CNN-based} facial gaze tracker, to enhance nervousness classification.}
        \resumeItem{Developed a fully automated local inference pipeline for video analysis with \textbf{PyTorch, OpenCV, dlib, and MediaPipe.}}
    \resumeItemListEnd

    \resumeProjectHeading
    {\projectHeadingColor\textbf{360Torrent} $|$ {Distributed Systems Engineer} $|$ \emph{\color{Black} Python (asyncio), Ansible, tmux, P2P Systems, BitTorrent}}{}
    \resumeItemListStart
        \resumeItem{Developed a \textbf{Python-based P2P CDN} for 360° video, reducing download latency by 42\% via geo-aware chunk prioritization.}
        \resumeItem{Designed churn-resilient downloader using \textbf{asyncio}, adaptive health checks, and rarest-first strategy; improved reliability by 35\%.}
        \resumeItem{Deployed system on 20 VMs using \textbf{tmux, tc, and Ansible,} simulating 100+ clients with region-aware network conditions.}
        \resumeItem{Integrated popularity matrix at tracker; pre-seeded hot chunks across peers, cutting startup latency by 28\%.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-1em}

%-----------SKILLS-----------%
\section{SKILLS}
{\fontsize{10}{12}\selectfont
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{@{\hspace{0.10in}}p{4cm}X@{}}
    \textbf{Mobile Development:} & iOS \{SwiftUI, CoreML, CocoaPods\}, Android \{Java\} \\
    \textbf{Languages:} & Java, Swift, Python, C/C++, TypeScript \\
    \textbf{Development:} & Object-Oriented Design, Software System Design, MVVM Architecture \\
    \textbf{Tools \& Frameworks:} & Git, JUnit 5, Spring Batch, Firebase \{Auth, Firestore\}, CoreData \\
    \textbf{Cloud Services:} & AWS \{CDK, Lambda, SQS, S3, CloudWatch\}
\end{tabularx}
} 

\vspace{-1em}

%-------------------------------------------%
\end{document}